---
title: 'Web Data: APIs and Scraping'
author: "Jinru Zhang"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
  pdf_document:
    number_sections: yes
    toc: no
    toc_depth: '4'
urlcolor: blue
---

```{r}
require("rgdax")
require("httr")
require("dplyr")
require("lubridate")
require("quantmode")
require("pbapply")
require("devtools")
# install.packages("rgdax")
library(rgdax)
library(keyring)
# Set API Keys and Account ID
library(httr)
library(ggplot2)
library(tidyverse)

# usethis::edit_r_environ()
# key_set("CBP_API_KEY") 
key_get("CBP_API_KEY") 
# key_set("CBP_PASS")
key_get("CBP_PASS") 
#key_set("CBP_SECRET") 
key_get("CBP_SECRET") 

# Check account balance
AllAccts <- accounts(api.key = key_get("CBP_API_KEY") ,
                            secret = key_get("CBP_SECRET"),
                            passphrase = key_get("CBP_PASS"))

head(AllAccts)
```

- Identify the link to instructions to obtain a key for the API


```{r echo=T, results='hide'}
#ETH and BTC currency price history
ETH_Stats <- public_candles("ETH-USD", start = "2020-12-31", end = "2021-09-30",granularity = 86400)
BTC_Stats <- public_candles("BTC-USD", start = "2020-12-31", end = "2021-09-30",granularity = 86400)
```

```{r}
ETH_table <-  as.data.frame(fromJSON(rawToChar(ETH_Stats$content)))
BTC_table <-  as.data.frame(fromJSON(rawToChar(BTC_Stats$content)))
colnames(ETH_table) <- c("time", "low", "high", "open", "close", "volume")
colnames(BTC_table) <- c("time", "low", "high", "open", "close", "volume")

head(ETH_table)
head(BTC_table)

ETH_table$time <-
  as.POSIXct(ETH_table$time, origin = "1970-01-01", tz = "GMT")
BTC_table$time <-
  as.POSIXct(ETH_table$time, origin = "1970-01-01", tz = "GMT")


# Add return and cumulative return column
ETH_table <- tibble(ETH_table) %>%
  arrange(time)

ETH_table <- ETH_table %>%
  mutate(return = c(0,diff(ETH_table$close)/ETH_table$close[-length(ETH_table$close)]))%>%
  mutate(cumu_ret = cumprod(1 + return))

BTC_table <- tibble(BTC_table) %>% 
  arrange(time) 
BTC_table <- BTC_table %>%
  mutate(return = c(0,diff(BTC_table$close)/BTC_table$close[-length(BTC_table$close)])) %>%
  mutate(cumu_ret = cumprod(1 + return)) 

ETH_BTC_cumu_ret_table <- tibble(data.frame(ETH_table$time, ETH_table$cumu_ret, BTC_table$cumu_ret))
names(ETH_BTC_cumu_ret_table) <- c("time", "ETH_Cumu_Ret", "BTC_Cumu_Ret")

ETH_BTC_cumu_ret_plot <- ETH_BTC_cumu_ret_table %>%
  select(time, ETH_Cumu_Ret, BTC_Cumu_Ret) %>%
  gather(key = "variable", value = "value", -time)
head(ETH_BTC_cumu_ret_plot)

ggplot(data = ETH_BTC_cumu_ret_plot, aes(x = time, y = value)) +
  geom_line(aes(color = variable,linetype = variable))+
  xlab("Date") + ylab("Cumulative Return") + theme_bw() +
  ggtitle("BTC and ETH cumultive return YTD by 2021Q3") +
  scale_color_manual(values = c("Orange", "steelblue"))

```

Conclusion:  From the plot, we can see ETH has cumulative return of about 300% while BTC only has cumulative return of 50%.

# IMDB List of Best Foreign Films

IMDB has a list of the [Top 100 Best Foreign Films](https://www.imdb.com/list/ls062615147/). This question requires scraping the following elements from the webpage and creating a tibble with all of these elements.  

- Number
- Title
- Year
- MPAA Rating
- Length in minutes
- Genre
- Star Rating
- Metascore Rating
- Gross Receipts
- Votes

```{r}
library(rvest)
html_obj <- read_html("https://www.imdb.com/list/ls062615147/")
hw_req_elements <- html_nodes(html_obj, 
                              css = ".mode-detail .list-description p , .text-muted .text-muted+ span , .text-muted a:nth-child(1) , .favorable , .ipl-rating-star.small .ipl-rating-star__rating , .genre , .runtime , .certificate , .unbold , .lister-item-header a")
tail(hw_req_elements,20)



```

  - b. Create a new variable with the text from each element
```{r}


hw_req_elements_text <- html_text(hw_req_elements)
length(hw_req_elements_text)

useful_elements <- hw_req_elements_text[130:length(hw_req_elements_text)]
head(useful_elements,20)
### Missing items
length(useful_elements) # 1095 not 1200 expected

```

  - c. Create a tibble from the text and remove any extra white space in the text.
```{r}
datadf <- tibble(text = useful_elements)
# datadf <- tibble(text = str_squish(useful_elements))
head(datadf)

#I do not want to remove extra white space in the text for now because I would like to use this as a rule to detect the information
```
Reason not to move extra spaces: I do not want to remove extra white space in the text for now because I would like to use this as a rule to detect the information.




  - d. Create logical variables to uniquely identify the rows for each variable. Discard any non-movie-related data prior to the first row with movie data.
```{r}
### Get the movie rank,movie name,and first director only, it will be used in later stage
ranking_elements <- html_nodes(html_obj, 
                               css = ".text-muted a:nth-child(1) , .lister-item-header a , .text-primary")
head(ranking_elements)

# To extract the text inside the obtained nodes, use html_text()
ranking_text <- html_text(ranking_elements)
head(ranking_text)
length(ranking_text)
# tibble tidy data

tibble(text = ranking_text) %>%
  dplyr::mutate(rownum = row_number(),
         ismovierank = rownum %% 3 == 1,
         isname = rownum %% 3 == 2,
         isdirector = rownum %% 3 == 0,
         movienum = rep(1:100, each = 3)) %>%
  select(-rownum) %>%
  mutate(key = case_when(ismovierank ~ "rank",
                         isname ~ "name",
                         isdirector ~ "director_first")) %>%
  select(key, text, movienum) %>%
  pivot_wider(names_from = key, values_from = text) %>% 
  select(-movienum) %>%
  mutate(rank = parse_number(rank)) ->
  movierank
head(movierank)
```
```{r}
# Step 1: Check if rank is missing
# Find rules Rankings are always of the form "\\d+\\." ie: 1. , 2. , 3. ...
# use this pattern and a cumulative sum 
# to figure out to which movies the elements belong.

datadf <- datadf %>%
  mutate(ismovierank = str_detect(text, "^\\d+\\.$")) 

head(datadf,20)
sum(datadf$ismovierank) 

## Conclusion=> Movie ranking is not missing

# Add a column indicate movie id
datadf <- datadf %>%
  mutate(movienum = cumsum(ismovierank)) %>%
  filter(movienum > 0)

head(datadf)

# Step 2: Check if movie name is missing
# Identify movie name from the previous cleaned movierank dataframe:
datadf <- datadf %>%
  mutate(isname = text %in% movierank$name)

sum(datadf$isname)

## Conclusion=> Movie name is not missing

# Step 3: Check if Year is missing
## Years are surrounded by parentheses

datadf <- datadf %>%
  mutate(isyear = str_detect(text, "\\(\\d+\\)"))

## make sure it is 100
sum(datadf$isyear)

## Conclusion=> Movie year is not missing

# Step 4: Check if MPAA Rating is missing
# 4.1 find unique MPAA Rating
MPAA <- html_nodes(html_obj, css = ".certificate")
MPAA <- unique(html_text(MPAA))

# 4.2 add column to check if MPAA rating is missing
datadf <- datadf %>%
  mutate(isMPAA = text %in% MPAA)

sum(datadf$isMPAA)

## Conclusion=> 15 of Movie MPAA Ratings are missing

# Step 5: Check if Movie length is missing
## movie length is number + space + letters

datadf <- datadf %>%
  mutate(islength = str_detect(text, "^\\d+[:space:][:lower:]"))

sum(datadf$islength)
## Conclusion=> Movie length is not missing

# Step 6: Check if Genre is missing
## each genre begins with a new line tag
datadf <- datadf %>%
  mutate(isgenre = str_detect(text, "^\\n")) 

## make sure it is 100
sum(datadf$isgenre)

## Conclusion=> Movie genre is not missing

# Step 7: Check if imdb_score is missing
## imdb_score: either digit+.+digit or just one digit
## Reason it work: assume the vote is always larger than 10, so single digit will work here

datadf <- datadf %>%
  mutate(isimdb_score = str_detect(text, "^\\d\\.\\d$") | str_detect(text, "^\\d$") )
sum(datadf$isimdb_score)         

## Conclusion=> Movie imdb score is not missing


# Step 8: Check if Metascore is missing
## metascore start by number and has many space at end
datadf <- datadf %>%
  mutate(ismetascore = str_detect(text, "^\\d+\\s+$")) 

sum(datadf$ismetascore) #48 of Movie Metascores are missing

## Conclusion=> Movie metascore has missing of 48

# Step 9: Check if votes is missing  
## votes: either digit + , digit + , +digit or digit + , +digit

datadf <- datadf %>%
  mutate(isvote = isimdb_score != TRUE & 
           (str_detect(text, "^\\d+\\,\\d+\\,\\d+$") | 
           str_detect(text, "^\\d+\\,\\d+$") | 
           str_detect(text, "^\\d+$")))
sum(datadf$isvote)     

## Conclusion=> Movie votes is not missing

# Step 10: Check if gross receipt is missing 
# Gross receipt ending by M
datadf <- datadf %>%
  mutate(isreceipt = str_detect(text, "M$"))
sum(datadf$isreceipt) 
## Conclusion=> Gross receipt has missing of 42

# Step 11: Check if Country is missing 
datadf <- datadf %>%
  mutate(iscountry = str_detect(text, "^From"))
sum(datadf$iscountry) 
## Conclusion=> Country is not missing


# Step 12: Check if First Director is missing 
# Identify First Director from the previous cleaned movierank dataframe:
datadf <- datadf %>%
  mutate(isfirst_dir = text %in% movierank$director_first)

sum(datadf$isfirst_dir)
## Conclusion=> First Director is not missing

head(datadf,22)
```


```{r}
missing_func <- function(data){
  return(100 - sum(data))
}

datadf %>% 
  select(ismovierank, 
         isname,
         isyear,
         isMPAA,
         islength,
         isgenre,
         isimdb_score,
         ismetascore,
         isvote,
         isreceipt,
         iscountry,
         isfirst_dir) %>%
  dplyr::summarise(across(.fns = missing_func))
```

Metascore, Gross Receipt and MPAA Rating are missing the most from the movie.
And the total missing is 105, matches my initial expection.



```{r}
datawide <- datadf %>%
  mutate(key = case_when(ismovierank ~ "rank",
                         isname ~ "name",
                         isyear ~ "year",
                         isMPAA ~ "MPAA",
                         islength ~ "length",
                         isgenre ~ "genre",
                         isimdb_score ~ "starscore",
                         ismetascore ~ "metacscore",
                         isvote ~ "vote",
                         isreceipt ~ "gross_receipts",
                         iscountry ~ "Country",
                         isfirst_dir ~ "first_director")) %>%
  select(key, text, movienum) %>%
  pivot_wider(names_from = key, values_from = text)

head(datawide)
```




```{r}
datawide <- datawide %>%
  mutate(rank = parse_number(rank),
         name = str_squish(name),
         year = parse_number(year),
         MPAA = as.factor(MPAA),
         length = parse_number(length),
         genre = str_replace_all(genre, "\\n", ""),
         genre = str_squish(genre),
         starscore = parse_number(starscore),
         metacscore = parse_number(metacscore),
         vote = parse_number(vote),
         gross_receipts = parse_number(gross_receipts),
         Country = as.factor(str_sub(Country, start = 6)),
         first_director = str_squish(first_director)) %>%
  select(-movienum)
  
head(datawide)
```



```{r}
datawide %>%
  group_by(MPAA) %>%
  dplyr::mutate(MPAA_Count = n()) %>%
  rowwise() %>%
  filter(MPAA_Count >= 4) %>%
  ggplot(aes(x = length, y = gross_receipts, color = MPAA)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE)
```
  

It appears only for PG-13 and PG rating, there is a positive linear relationship
between length of a film and its gross revenue.
There are also appears to have a positive linear relationship
between length of a film and its gross revenue for MPAA Not Rated movie.


 

```{r}
datawide %>%
  group_by(MPAA) %>%
  dplyr::mutate(MPAA_Count = n()) %>%
  rowwise() %>%
  filter(MPAA_Count >= 4, metacscore >= 50, metacscore <= 100) %>%
  ggplot(aes(x = metacscore, y = starscore)) +
  geom_point(aes( color = MPAA)) 
```


```{r}
datawide %>%
  group_by(MPAA) %>%
  dplyr::mutate(MPAA_Count = n()) %>%
  rowwise() %>%
  filter(MPAA_Count >= 4, metacscore >= 50, metacscore <= 100) %>%
  ggplot(aes(x = metacscore, y = starscore)) +
  geom_point(aes( color = MPAA)) +
  geom_smooth(formula = y ~ x, method = "lm", se = FALSE)
```



```{r}
datawide_lm <-  datawide[which(datawide$metacscore >= 50),]
lm_model <- lm(starscore~metacscore, data = datawide_lm)
summary(lm_model)
```

I am surprised at the result since the p-value of the regression is 0.0618 > 0.05 and adjusted R
Squared is very small at 0.0494. It means the overall model is not significantly meaningful.
However, the plot shows there appear to be positive relationship between metascore and star score.

I think it might because the variance of metascore is too large.Another reason could be there are a few outliers. For example, in the chart, I can see a few movies has quite high metascore but fairly low star score or low metascore but high star score.



```{r}
datawide %>%
  ggplot(aes(x = vote, y = reorder(Country,vote,FUN = mean))) +geom_boxplot() + 
  ylab("") +xlab("Votes") + ggtitle("IMDB Votes per Top 100 Foreign Films \n by Country") +
  theme_light() 
  
```


The chart ranked country by the movies average votes in the country. From the chart, we can see Brazil's movies on average has the highest votes. And a few countries including France, Italy, Spain, South Korea and Japan have a few movies has extraordinary high votes. 




```{R}
datawide %>%
  group_by(first_director) %>%
  dplyr::mutate(num_movies = n(),
         total_gross = sum(gross_receipts, na.rm = T)) %>%
  select(first_director,num_movies, total_gross) %>%
  unique() %>%
  arrange(desc(num_movies)) %>%
  head(5)

# The top 5 first directors with largest total number of movies are:
# Park Chan-Wook, Jean-Luc Godard, Hayao Miyazaki, Federico Fellini, Pedro Almodóvar
```
- Identify the top 5 first directors based on their total gross and the number of movies

```{R}
datawide %>%
  group_by(first_director) %>%
  dplyr::mutate(num_movies = n(),
         total_gross = sum(gross_receipts, na.rm = T)) %>%
  select(first_director,num_movies, total_gross) %>%
  unique() %>%
  arrange(desc(total_gross)) %>%
  head(5)
# The top 5 first directors with largest total gross are:
# Roberto Benigni, Guillermo del Toro, Jean-Pierre Jeunet, Alfonso Arau, Federico Fellini
```
- By just looking at the results, which director appears on both lists?
Only director Federico Fellini appears on both lists

